---
title: "secuTrialRshiny - a walkthrough"
author: "Patrick R. Wright, Milica Markovic, Alan Haynes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
toc: true
vignette: >
  %\VignetteIndexEntry{secuTrialR-package-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

\newpage

# Introduction

This R package provides functions for creating and running a Shiny web application 
for handling data from the clinical data management system (CDMS) 
[\textcolor{blue}{secuTrial}](https://www.secutrial.com/en/). This package builds on SCTO's data management R package [secuTrialR](https://github.com/SwissClinicalTrialOrganisation/secuTrialR).
The package is developed and maintained by the Swiss Clinical Trial Organisation
([\textcolor{blue}{SCTO}](https://www.scto.ch/en/news.html)).

This vignette will teach you how to use the `secuTrialRshiny` package.

```{r, include = FALSE}
# needed so that the as.data.frame part of the vignette
# does not need a restart of the session everytime the
# vignette is built
rm(list = ls())
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installing

Let's get started by installing the package straight from 
[\textcolor{blue}{GitHub}](https://github.com/SwissClinicalTrialOrganisation/secuTrialRshiny)
and then loading it. For this you will need to have `devtools` installed. 
\vspace{5pt}

```{r, eval = FALSE}
# install
devtools::install_github("SwissClinicalTrialOrganisation/secuTrialRshiny")
```

To run the app localy on your computer after installation, run

```{r, eval = FALSE}
secuTrialRshiny::run_shiny()
```

# Disclaimer
The descriptions of the secuTrial exports used in this vignette and other `secuTrialR` and `secuTrialRshiny`
documentation correspond to our understanding of them and come with no warranty.
For in depth details please refer to the original secuTrial manuals.

# The `sessionInfo()`

```{r}
sessionInfo()
```


